---
title: "milestone_6"
author: "Connor Riordan"
date: "4/3/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library(tidyverse)
library(readxl)
library(janitor)
library(gt)
library(scales)
library(markdown)
```

```{r, include = FALSE}

# In this data, I decided to use head() and gt() in order to make the data look
# nice when knitting.

```

## Voting Age by Region 2016

```{r, age_by_region_voting_2016, echo = FALSE, message=FALSE, warning=FALSE}

# For this milestone, I didn't do much with this data because I have a question
# that I need to ask my TF, June, before I proceed with my data.

age_by_region_voting_2016 <- read_xlsx("Raw-data/age_by_region_voting_2016.xlsx", skip = 6) %>%
  clean_names()

age_by_region_voting_2016_revised <- age_by_region_voting_2016 %>%
  rename("Region" = x1,
         "Region Part" = x2,
         "Age" = x3, 
         "Total Population" = x4,
         "Total Citizen Population" = x5,
         "Reported Registered (Number)" = number_6,
         "Reported Registered (Percent)" = percent_7,
         "Reported Not Registered (Number)" = number_8,
         "Reported Not Registered (Percent)" = percent_9,
         "No Response (Number)" = number_10,
         "No Response (Percent)" = percent_11,
         "Reported Voted (Number)" = number_12,
         "Reported Voted (Percent)" = percent_13,
         "Reported Not Voted (Number)" = number_14,
         "Reported Not Voted (Percent)" = percent_15,
         "No Response to Voting (Number)" = number_16,
         "No Response to Voting (Percent)" = percent_17,
         "Reported Registered" = percent_18,
         "Reported Voted" = percent_19)

northeast_total <- age_by_region_voting_2016_revised %>%
  select(-c(`Region`, `Region Part`)) %>%
  slice(2:7)

northeast_total_plot <- northeast_total %>%
  ggplot(aes(Age, `Total Population`)) + geom_bar(stat = "identity")

northeast_total_plot
```

## Age Characteristics of Voters 2018

```{r, age_characteristics_voting_2018, echo = FALSE, message=FALSE, warning=FALSE}

# With this data, I tried figuring out how to swithch the character/list 
# variables to numeric so I would be able to plot them with ggplot. 
# Unfortunately, this is another set of data where I have to ask June,
# since as.numeric did not work. However, I did put it into a pretty
# ggplot!

# use col_types to specify what value you want your columns to be.

age_characteristics_voting_2018_numeric <- read_xlsx("Raw-data/age_characteristics_voting_2018.xlsx", skip = 2, col_types = "numeric") %>%
  clean_names() %>%
  select(!c(state_abbreviation, state_name, congressional_district))

age_characteristics_voting_2018_character <- read_xlsx("Raw-data/age_characteristics_voting_2018.xlsx", skip = 2, col_types = "text") %>%
  clean_names() %>%
  select(c(state_abbreviation, state_name, congressional_district))

age_characteristics_voting_2018 <- cbind(age_characteristics_voting_2018_character, age_characteristics_voting_2018_numeric)%>%
  drop_na() 

state_total_voting_age_pop <- age_characteristics_voting_2018 %>%
  ggplot(aes(x = state_name, y = citizen_voting_age_population)) + geom_col(stat = "identity") +
  theme(axis.text.x = element_text(angle = 90))


```
## Unused (but needed) code

%>%
  rename("Total Voting Age Population (estimate)" = citizen_voting_age_population,
         "Total Age 18-29 (estimate)" = age,
         "Total Age 30-44 (estimate)" = x11,
         "Total Age 45-64 (estimate)" = x15,
         "Total Age 65+ (estimate)" = x19,
         "Margin of error (MOE)" = x6, 
         "Margin of error (MOE) 18-29" = x8, 
         "Margin of error (MOE) 30-44" = x12, 
         "Margin of error (MOE) 45-64" = x16, 
         "Margin of error (MOE)65+" = x20,
         "Percent of total 18-29" = x9, 
         "Percent of total 30-44" = x13, 
         "Percent of total 45-64" = x17, 
         "Percent of total 65+" = x21,
         "Percent of total margin of error (MOE) 18-29" = x10, 
         "Percent of total margin of error (MOE) 30-44" = x14, 
         "Percent of total margin of error (MOE) 45-64" = x18, 
         "Percent of total margin of error (MOE) 65+" = x22)





age_characteristics_voting_2018_revised %>%
  cols_merge(columns = vars(state_name, congressional_district),
             pattern = "{1}&mdash;{2}") %>%
  cols_hide(columns = vars(line_number, state_abbreviation)) %>%
  cols_label(state_name = "State and Congressional District")


## Civic Education Requirements by State

```{r, civic_education_requirements_by_state, echo = FALSE, message=FALSE, warning=FALSE}

# I still need to figue out what I want to do with this data - possibly a join,
# perhaps I'll keep it in a gt() table, I am not sure. Unfortunately, this is
# not the kind of data that I want to put into a ggplot because it looks ugly.

civic_education_requirements_by_state <- read_csv("Raw-data/civic_education_requirements_by_state.csv") %>%
  clean_names()

civic_education_requirements_by_state_revised <- civic_education_requirements_by_state %>%
  select(-"notes") %>%
  gt()

civic_education_requirements_by_state_revised

```

## Votes Cast by Voting Age 2018

```{r, votes_cast_voting_age_2018, echo = FALSE, message=FALSE, warning=FALSE}

# For this milestone, I took the data and put it into three separate ggplots -
# one for the entire US by state abbreviation, one for just the congressional
# districts of Alabama, and one for the congressional districts of Alaska.
# The plots look beautiful, if I do say so myself. This is what I want to do 
# for every state, although hopefully there will be a way to replicate the
# process that is not as time-consuming and painful.

votes_cast_voting_age_2018_numeric <- read_xlsx("Raw-data/votes_cast_voting_age_2018.xlsx", col_types = "numeric", skip = 2) %>%
  clean_names() %>%
  select(!c(state_abbreviation, state_name, congressional_district))

votes_cast_voting_age_2018_character <- read_xlsx("Raw-data/votes_cast_voting_age_2018.xlsx", col_types = "text", skip = 2) %>%
  clean_names() %>%
  select(c(state_abbreviation, state_name, congressional_district))

votes_cast_voting_age_2018 <- cbind(votes_cast_voting_age_2018_character, votes_cast_voting_age_2018_numeric) %>%
  drop_na()

votes_cast_voting_age_2018_revised <- votes_cast_voting_age_2018 %>%
  select(-line_number) %>%
  drop_na() %>%
  rename("Votes Cast" = votes_cast_for_congressional_representative_for_the_november_6_2018_election1, 
         "Number of Eligible Citizens (Estimate)" = citizen_voting_age_population2,
         "Margin of Error for Eligible Citizens" = x7,
         "Voting Rate" = voting_rate3,
         "Margin of Error for Voting Rate" = x9)

by_abbreviation <- votes_cast_voting_age_2018_revised %>%
  ggplot(aes(state_abbreviation, `Votes Cast`)) + geom_bar(stat = "identity") +
  labs(
    title = "Votes Cast by Voting Age 2018",
    x = "State (Abbreviated)"
  ) +
  scale_y_continuous(labels = comma) +
  theme_bw() +
  theme(axis.text.x = element_text(angle = 90))

by_abbreviation


by_congressional_district_AL <- votes_cast_voting_age_2018_revised %>%
  filter(state_name == "Alabama") %>%
  ggplot(aes(congressional_district, `Votes Cast`)) + geom_bar(stat = "identity") +
  labs(
    title = "Votes Cast by Voting Age 2018",
    subtitle = "Alabama"
  ) +
  scale_y_continuous(labels = comma) +
  theme_bw()

by_congressional_district_AL

by_congressional_district_AK <- votes_cast_voting_age_2018_revised %>%
  filter(state_name == "Alaska") %>%
  ggplot(aes(congressional_district, `Votes Cast`)) + geom_bar(stat = "identity", width = 0.5) +
  labs(
    title = "Votes Cast by Voting Age 2018",
    subtitle = "Alaska"
  ) +
  scale_y_continuous(labels = comma) +
  theme_bw()

by_congressional_district_AK

```

## Recorded Voting by Age 2016

```{r, recorded_voting_by_age_2016, echo = FALSE, message=FALSE, warning=FALSE}

# Like the data before this one, I wanted to divide this by both the US
# and by each state so we can examine the age groups from all of these separate
# samples. I hope to replicate the plot for every state that is included in the
# data set, once again hopefully finding a way to do this without typing out
# the same code time and again.

recorded_voting_by_age_2016 <- read_xlsx("Raw-data/recorded_voting_by_age_2016.xlsx", skip = 2) %>%
  clean_names()

recorded_voting_by_age_2016_revised <- recorded_voting_by_age_2016 %>%
  rename("State" = in_thousands,
         "Age" = x2,
         "Total Population" = x3,
         "Total Citizen Population" = x4,
         "Total Registered" = x5,
         "Total Registered (Percent)" = x6,
         "Margin of Error (MOE)" = x7,
         "Percent Registered (Citizen)" = x8,
         "MOE" = x9,
         "Total Voted" = x10,
         "Total Voted (Percent)" = x11,
         "MOE_3" = x12,
         "Percent Voted (Citizen)" = x13,
         "MOE_4" = x14)


US <- recorded_voting_by_age_2016_revised %>%
  select(-State) %>%
  slice(4:8)

US_recorded_voting_by_age <- US %>%
  ggplot(aes(Age, `Total Population`)) + geom_bar(stat = "identity") +
  labs(
    title = "Recorded Voting by Age 2016",
    subtitle = "United States"
  ) +
  theme_bw()

US_recorded_voting_by_age

Alabama <- recorded_voting_by_age_2016_revised %>%
  select(-State) %>%
  slice(8:12)

Alabama_recorded_voting_by_age <- Alabama %>%
  ggplot(aes(Age, `Total Population`)) + geom_bar(stat = "identity") +
  labs(
    title = "Recorded Voting by Age 2016",
    subtitle = "Alabama"
  ) +
  theme_bw()

Alabama_recorded_voting_by_age

```


```{r, voting_by_age_sex_nov_2018, echo = FALSE, message = FALSE, error = FALSE}

# This is more data that I wanted to include in my project. I think it's
# important to include as much voting information as possible from a number
# of different years so it is possible to compare voting patterns and map
# civic education to those patterns. With this data I also had a paroblem
# turning character variables into numeric variables so I am hoping June
# will be able to assist me with that as well.

v <- read_xlsx("Raw-data/voting_by_age_sex_nov_2018.xlsx")

voting_by_age_sex_nov_2018_numeric <- read_xlsx("Raw-data/voting_by_age_sex_nov_2018.xlsx", col_types = "numeric") %>%
  clean_names() %>%
  select(!c("table_with_row_headers_in_columns_a_and_b_and_column_headers_in_rows_5_through_7", "x2"))

voting_by_age_sex_nov_2018_character <- read_xlsx("Raw-data/voting_by_age_sex_nov_2018.xlsx", col_types = "text") %>%
  clean_names() %>%
  select("x2")

voting_by_age_sex_nov_2018 <- cbind(voting_by_age_sex_nov_2018_character, voting_by_age_sex_nov_2018_numeric) %>%
  drop_na()

voting_by_age_sex_nov_2018_revised <- voting_by_age_sex_nov_2018 %>%
  rename(
    "Age" = x2,
    "Total Population" = x3,
    "Total Citizen Population" = x4,
    "Reported Registered" = x5,
    "Percent Recorded Registered" = x6,
    "Recorded Not Registered" = x7,
    "Percent Recorded Not Registered" = x8,
    "No Response to Registration" = x9,
    "Percent No Response to Registration" = x10,
    "Reported Voted" = x11,
    "Percent Reported Voted" = x12,
    "Reported Not Voted" = x13,
    "Percent Reported Not Voted" = x14,
    "No Response to Voted" = x15,
    "Percent No Response to Voted" = x16,
    "Total Reported Registered Percent" = x17,
    "Total Voted Percent" = x18
  )


voting_by_age_sex_nov_2018 %>%
  ggplot(aes(x2, x3)) + geom_bar(stat = "identity") +
  labs(
    title = "Voting by Age for Both Sexes",
    subtitie = "Total Population",
    x = "Age Group",
    y = "Population"
  ) + theme_bw() + theme(axis.text.x = element_text(angle = 90))


```









